\textls[-0]{\thetitle}

### 2023-03-16 canonicitymodel.tex
Save more on canonicity model.

Thus, we define a new denotation $\denotesCC{S} \coloneq (S, \denotesC{S})$, that will return the syntax piece $S$ as well. Thus we can have a function $\Glued{\Pi}$ s.t. $\GluedPi{\denotesCC{A}}{\denotesCC{B}} = \denotesCC{\TyPi{A}{B}}$ now that syntax is also provided. Similarly, we can have $\Glued{\Sigma}$, $\Gpair{a}{b}$  and $\GSubstExt{\gm}{t}$  for dependent tuple type, depende tuple construction and substitution extension, and also all other constructions.  What's more, given $\Glued{S}$ a pair of syntax and model , we denote $\Gmodel{\Glued{S}}$ as getting the (canonicity) model part (the second element in that pair).  
% These will be useful in our \TT model because as syntactic translation hinted, \TT reuses a lot from MLTT. What's more, during the construction of the model for \TT, we will use $\Glued{(\cdot)}$ when we can.

@@

  \denotesC{\goodWSig{\Gm}{\wsig}{n}} &\text{ is a list of 2-tuple of length $n$ } \\

@@

>>>>

Thus, we define a new denotation $\denotesCC{S} \coloneq (S, \denotesC{S})$, that will return the syntax piece $S$ as well.\footnote{This is also called glued interpretation in \citet{sterling2019algebraic}} Thus we can have a function $\Glued{\Pi}$ s.t. $\GluedPi{\denotesCC{A}}{\denotesCC{B}} = \denotesCC{\TyPi{A}{B}}$ now that syntax is also provided. Similarly, we can have $\Glued{\Sigma}$, $\Gpair{a}{b}$  and $\GSubstExt{\gm}{t}$  for dependent tuple type, depende tuple construction and substitution extension, and also all other constructions.  What's more, given $\Glued{S}$ a pair of syntax and model , we denote $\Gmodel{\Glued{S}}$ as getting the (canonicity) model part (the second element in that pair).  
% These will be useful in our \TT model because as syntactic translation hinted, \TT reuses a lot from MLTT. What's more, during the construction of the model for \TT, we will use $\Glued{(\cdot)}$ when we can.

\newcommand{\GTy}[2]{\ensuremath{\Glued{\texttt{Ty}}_{#1}~{#2}}}
\newcommand{\GCon}[1]{\ensuremath{\Glued{\texttt{Con}}_{#1}}}
\newcommand{\GMWSig}[3]{\ensuremath{{\texttt{WSig}^C}_{#1}^{#3}~{#2}}}
\newcommand{\GWSig}[3]{\ensuremath{{\Glued{\texttt{WSig}}}_{#1}^{#3}~{#2}}}

There are actually more \emph{internal} type-theoretic construction to explore, and we need them to define the model for \TT as well.

We denote $\GCon{k} \coloneq \sum_{\goodCtx{\Gm}{k}} \{\gm : \goodSub{\cdot}{\gm}{\Gm} \} \to \Set{k}$

and $\GTy{j}{\Glued{\Gm}} \coloneq \sum_{\goodType{\Gm}{T}{j}} \prod_{\goodSub{\cdot}{\gm}{\Gm}}\prod_{\gm' \in \Gmodel{\Glued{\Gm}}(\gm)}\{t : \goodTerm{\cdot}{t}{\sub{T}{\gm}}\}\to\Set{j} $ for $\Glued{\Gm} \in \GCon{k}$.

Basically the point is, for each well-typed type $\goodType{\Gm}{T}{j}$,  we have its denotation $\denotesCC{T} \in \GTy{j}{\denotesCC{\Gm}}$.

Then we define $\GMWSig{j}{\Glued{\Gm}}{n} \coloneq "Vector"^n~\sum_{\Glued{A} \in \GTy{j}{\Glued{\Gm}}} \GTy{j}{(\GSubstExt{\Glued{\Gm}}{\Glued{A}})}$ for $\Glued{\Gm} \in \GCon{k}$, which is basically a list of a pair of types of length $n$. As before, we can define glued interpretation $\GWSig{j}{\Glued{\Gm}}{n} \coloneq \{ \wsig : \goodWSig{\cdot}{\wsig}{n} \} \times \GMWSig{j}{\Glued{\Gm}}{n}$. This will be useful when we interpret judgement for W-type signature.

@@

  \denotesC{\goodWSigU{j}{\Gm}{\wsig}{n}} &: \GMWSig{j}{\denotesCC{\Gm}}{n} \\ 
    &\text{ i.e., a list of 2-tuple of length $n$ } \\

@@

together with the following inductively defined indexed set and its eliminator principle. These can be directly translated into Agda but we use a more conventional math notation
  "Inductive"~CW_p : (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    "CWsup"_p : n < N \to 
